ST563 Final Project

### 2021-03-11 ST563-FP.Rmd
started boosted tree description

## Boosting

## Multiple Linear Regression

>>>>

## Boosted Tree
Boosting is the process of slowly training trees to avoid overfitting. The general approach is as follows: the trees are grown sequentially, where each subsequent tree is grown on a modified version of the original data, while the predictions are continuously updated as the trees are grown. The model has three parameters that need tuning:

  * $B$ - the number of trees
  * $\lambda$ - the shrinkage parameter, which is a small positive number that controls the rate at which the boosting learns
  * $d$ - the number of splits in each tree, which controls the complexity of the boosted ensemble

The main benefit of using boosting is to reduce overfitting. It often yields the best results in terms of the ensemble learning methods. 
## Multiple Linear Regression
